Scaffolder - Software for Microbial Genome Scaffolding.

### 2011-01-28 text/src/article.tex
Command line interface section of results

  * Illustrate running command line to generate output
  * Demonstrate scaffold validate to test inserts overlap

\subsubsection*{Accessible programmatic interface} %{{{3

@@

\section*{Availability and Requirements}

@@

% }}}
% {{{ Author's Information
\section*{Authors contributions}
    Text for this section \ldots
% }}}
% {{{ Acknowledgements
\section*{Acknowledgements}
  \ifthenelse{\boolean{publ}}{\small}{}
  Text for this section \ldots
%}}} {{{1 Bibliography
{\ifthenelse{\boolean{publ}}{\footnotesize}{\small}
 \bibliographystyle{bmc_article}  % Style BST file
  \bibliography{article} }     % Bibliography file (usually '*.bib' )

>>>>

Scaffolder provides a command line interface to validate and build a genome
sequence from a scaffold. Assuming scaffolder has been installed and the
binary is available in the command line path the following command can be used
to invoke scaffolder. This will list the available commands for running
scaffolder.

\begin{verbatim}
$ scaffolder
\end{verbatim}

Help on each command can be found by type `help' followed by the name of the
command. This will return the Unix manual page for the command of interest.
For example the following command will return the manual page for sequence
listing the available options for running the sequence command.

\begin{verbatim}
$ scaffolder help sequence
\end{verbatim}

To the generate the fasta sequence from a scaffold the sequence command should
be used. This should be passed the name of the file with containing the YAML
formatted scaffold and the corresponding fasta file of sequences. This will
then return the complete drafted sequence to the standard out.

\begin{verbatim}
$ scaffolder sequence scaffold.yml sequences.fna
\end{verbatim}

Scaffolder also provides a function to test the scaffold for overlapping
insert sequence co-ordinates. As described in the section above overlapping
inserts will result in unexpected behaviour as the coordinates for the first
insert will change the expected insert location for the second insert. The
validate command will check the scaffold for any overlapping inserts and
return them as a YAML formatted list describing each one.

\begin{verbatim}
$ scaffolder validate scaffold.yml sequences.fna
\end{verbatim}

\subsubsection*{Application programming interface} %{{{3

@@

\section*{Availability and Requirements} %{{{1

@@

% }}}
% {{{ Author's Information
\section*{Authors contributions}
    Text for this section \ldots
% }}}
% {{{ Acknowledgements
\section*{Acknowledgements}
  \ifthenelse{\boolean{publ}}{\small}{}
  Text for this section \ldots
%{{{1 Bibliography
{\ifthenelse{\boolean{publ}}{\footnotesize}{\small}
 \bibliographystyle{bmc_article}  % Style BST file
  \bibliography{article} }     % Bibliography file (usually '*.bib' )
